---
title: "Lab 11 - Smoking during pregnancy"
author: "Ryan Wheat"
date: "4/5/2023"
output: github_document
---

### Load packages and data

```{r load-packages-and-data, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
data(ncbirths)
```

### Exercise 1

Each case is one baby in North Carolina. Thus, each variable describes something that applies to that baby: the age of their mother/father, their weight, etc. There are a total of 1,000 babies in this dataframe.

I created histograms for each continuous variable in order to see if there are any outliers that may muck up my analyses. There are a couple of outliers in each group, but I feel like I don't have any good reason to exclude them, so I should be conservative here and keep them in for my analyses.

```{r summary-variables}

summary(ncbirths)

#checking for outliers in numerical variables

ggplot(data = ncbirths, mapping = aes(x = fage)) + geom_histogram()
ggplot(data = ncbirths, mapping = aes(x = mage)) + geom_histogram()
ggplot(data = ncbirths, mapping = aes(x = weeks)) + geom_histogram()
ggplot(data = ncbirths, mapping = aes(x = visits)) + geom_histogram()
ggplot(data = ncbirths, mapping = aes(x = gained)) + geom_histogram()
ggplot(data = ncbirths, mapping = aes(x = weight)) + geom_histogram()
```


### Exercise 2

The average white baby weighs 7.25 pounds.

```{r create-new-dataframe}

#filter for white moms

ncbirths_white <- ncbirths %>%
  filter(whitemom == "white")

summary(ncbirths_white)

```


Add exercise headings as needed.
